Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-19 analysis/paper/paper.Rmd
Edits to main text

@@

We therefore established field experiments in order to determine what effects AWD could have on sheath blight disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B. Frank) Donk.] of rice.

Sheath blight is economically important worldwide and it is difficult to find resistance to the disease [@Srinivasachary2011]. Therefore management is usually a combination of cultural practices, which include nitrogen and water management. High nitrogen levels

>>>>

Sheath blight disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B. Frank) Donk.] of rice is economically important worldwide and difficult to find resistance to the disease [@Srinivasachary2011]. Therefore management is usually a combination of cultural practices, which include nitrogen and water management (citation).

@@

We therefore established field experiments in order to determine what effects AWD could have on sheath blight.
